Response to reviewers

### 2025-01-23 Manuscript/Tables/results_differences4d_3.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_1 & FI.ses\_1 & FI.d\_2 & FI.ses\_2 & FI.d\_3 & FI.ses\_3 & FI.d\_4 & FI.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 667.99*** & 1.31 & 871.01*** & 1.14 & 808.97*** & 0.83 & 549.73*** & 0.48 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 1625.13*** & 1.34 & 1706.46*** & 1.14 & 1401.89*** & 0.83 & 908.74*** & 0.49 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 398.17*** & 2.59 & 587.5*** & 2.44 & 586.06*** & 1.89 & 437.87*** & 1.12 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 33.97*** & 3.24 & 40.35*** & 3.04 & 36.06*** & 1.83 & 23.54*** & 1.03 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.05*** & 1.29 & 0.04*** & 1.08 & 0.02*** & 0.67 & 0.01*** & 0.31 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 1.16*** & 1.84 & 0.91*** & 1.4 & 0.67*** & 1.01 & 0.42*** & 0.62 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.1*** & 1.15 & 0.07*** & 0.83 & 0.04*** & 0.55 & 0.02*** & 0.32 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 1.83*** & 4.43 & 1.42*** & 4.4 & 1*** & 3.98 & 0.59*** & 3.23 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.01*** & 1 & 0.01*** & 1.18 & 0.01*** & 0.85 & 0*** & 0.34 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.04*** & -1.03 & -0.02*** & -0.87 & -0.01*** & -0.49 & -0.01*** & -0.25 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0* & -0.26 & 0 & -0.14 & 0 & 0.1 & 0 & 0.07 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.02*** & 0.88 & 0.01*** & 0.54 & 0* & 0.18 & 0 & 0.09 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:00 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_rm1 & FI.ses\_rm1 & FI.d\_rm2 & FI.ses\_rm2 & FI.d\_rm3 & FI.ses\_rm3 & FI.d\_rm4 & FI.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 667.99*** & 1.31 & 871.01*** & 1.14 & 808.97*** & 0.83 & 549.73*** & 0.48 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 1625.13*** & 1.34 & 1706.46*** & 1.14 & 1401.89*** & 0.83 & 908.74*** & 0.49 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 398.17*** & 2.59 & 587.5*** & 2.44 & 586.06*** & 1.89 & 437.87*** & 1.12 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 33.97*** & 3.24 & 40.35*** & 3.04 & 36.06*** & 1.83 & 23.54*** & 1.03 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.05*** & 1.29 & 0.04*** & 1.08 & 0.02*** & 0.67 & 0.01*** & 0.31 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 1.16*** & 1.84 & 0.91*** & 1.4 & 0.67*** & 1.01 & 0.42*** & 0.62 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.1*** & 1.15 & 0.07*** & 0.83 & 0.04*** & 0.55 & 0.02*** & 0.32 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 1.83*** & 4.43 & 1.42*** & 4.4 & 1*** & 3.98 & 0.59*** & 3.23 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.01*** & 1 & 0.01*** & 1.18 & 0.01*** & 0.85 & 0*** & 0.34 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.04*** & -1.03 & -0.02*** & -0.87 & -0.01*** & -0.49 & -0.01*** & -0.25 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0* & -0.26 & 0 & -0.14 & 0 & 0.1 & 0 & 0.07 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.02*** & 0.88 & 0.01*** & 0.54 & 0* & 0.18 & 0 & 0.09 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FI = FI; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences4d_4.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_1 & CO.ses\_1 & CO.d\_2 & CO.ses\_2 & CO.d\_3 & CO.ses\_3 & CO.d\_4 & CO.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 160.54*** & 0.28 & 239.24*** & 0.28 & 239.86*** & 0.23 & 181.09*** & 0.15 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 436.95*** & 0.3 & 491.69*** & 0.28 & 445.45*** & 0.24 & 307.31*** & 0.15 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 115.67*** & 0.61 & 153.13*** & 0.48 & 159.12*** & 0.42 & 123.17*** & 0.27 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 6.44*** & 0.69 & 8.26*** & 0.61 & 8.72*** & 0.52 & 6.84*** & 0.36 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.04*** & 0.93 & 0.03*** & 0.91 & 0.02*** & 0.7 & 0.01*** & 0.44 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.28*** & 0.41 & 0.24*** & 0.34 & 0.19*** & 0.28 & 0.13*** & 0.18 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.03*** & 0.35 & 0.02*** & 0.26 & 0.02*** & 0.23 & 0.01*** & 0.14 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.68*** & 2.23 & 0.59*** & 2.72 & 0.44*** & 2.8 & 0.28*** & 2.85 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0*** & 0.39 & 0.01*** & 0.61 & 0.01*** & 0.61 & 0*** & 0.39 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.01*** & -0.43 & -0.01*** & -0.38 & -0.01*** & -0.3 & 0*** & -0.22 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0 & -0.08 & 0 & -0.02 & 0 & -0.02 & 0 & -0.02 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.01*** & 0.48 & 0.01*** & 0.5 & 0.01*** & 0.48 & 0*** & 0.21 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:03 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_rm1 & CO.ses\_rm1 & CO.d\_rm2 & CO.ses\_rm2 & CO.d\_rm3 & CO.ses\_rm3 & CO.d\_rm4 & CO.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 160.54*** & 0.28 & 239.24*** & 0.28 & 239.86*** & 0.23 & 181.09*** & 0.15 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 436.95*** & 0.3 & 491.69*** & 0.28 & 445.45*** & 0.24 & 307.31*** & 0.15 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 115.67*** & 0.61 & 153.13*** & 0.48 & 159.12*** & 0.42 & 123.17*** & 0.27 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 6.44*** & 0.69 & 8.26*** & 0.61 & 8.72*** & 0.52 & 6.84*** & 0.36 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.04*** & 0.93 & 0.03*** & 0.91 & 0.02*** & 0.7 & 0.01*** & 0.44 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.28*** & 0.41 & 0.24*** & 0.34 & 0.19*** & 0.28 & 0.13*** & 0.18 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.03*** & 0.35 & 0.02*** & 0.26 & 0.02*** & 0.23 & 0.01*** & 0.14 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.68*** & 2.23 & 0.59*** & 2.72 & 0.44*** & 2.8 & 0.28*** & 2.85 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0*** & 0.39 & 0.01*** & 0.61 & 0.01*** & 0.61 & 0*** & 0.39 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.01*** & -0.43 & -0.01*** & -0.38 & -0.01*** & -0.3 & 0*** & -0.22 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0 & -0.08 & 0 & -0.02 & 0 & -0.02 & 0 & -0.02 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.01*** & 0.48 & 0.01*** & 0.5 & 0.01*** & 0.48 & 0*** & 0.21 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D).CO = CO; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences8d_1.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_1 & EQ.ses\_1 & EQ.d\_2 & EQ.ses\_2 & EQ.d\_3 & EQ.ses\_3 & EQ.d\_4 & EQ.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 761.11*** & 1.34 & 962.64*** & 1.11 & 873.68*** & 0.81 & 544.78*** & 0.43 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 1031482.51*** & 0.39 & 1415980.4*** & 0.33 & 1316657.33*** & 0.23 & 798612.09*** & 0.12 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 7348.88*** & 2.06 & 29098.27*** & 1.93 & 48535.88*** & 1.7 & 47957.63*** & 1.11 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 52.07*** & 3.25 & 62.28*** & 3 & 55*** & 2.41 & 33.6*** & 1.35 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.08*** & 2.07 & 0.05*** & 1.37 & 0.03*** & 0.72 & 0.01*** & 0.29 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 2*** & 2.46 & 1.49*** & 1.83 & 1.07*** & 1.27 & 0.62*** & 0.73 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.12*** & 1.6 & 0.08*** & 1.16 & 0.06*** & 0.85 & 0.03*** & 0.5 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 6.09*** & 12.85 & 4.25*** & 12.1 & 2.83*** & 10.04 & 1.56*** & 7.82 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0*** & 0.47 & 0*** & 0.43 & 0*** & 0.22 & 0 & -0.01 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.07*** & -4.87 & -0.03*** & -3.81 & -0.02*** & -2.76 & -0.01*** & -1.71 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0*** & -0.72 & 0*** & -0.42 & 0*** & -0.29 & 0*** & -0.25 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.02*** & 0.86 & 0.01*** & 0.47 & 0*** & 0.25 & 0 & 0.05 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:13 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_rm1 & EQ.ses\_rm1 & EQ.d\_rm2 & EQ.ses\_rm2 & EQ.d\_rm3 & EQ.ses\_rm3 & EQ.d\_rm4 & EQ.ses\_rm4 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 1031482.51*** & 0.39 & 1415980.4*** & 0.33 & 1316657.33*** & 0.23 & 798612.09*** & 0.12 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 7348.88*** & 2.06 & 29098.27*** & 1.93 & 48535.88*** & 1.7 & 47957.63*** & 1.11 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 52.07*** & 3.25 & 62.28*** & 3 & 55*** & 2.41 & 33.6*** & 1.35 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 2*** & 2.46 & 1.49*** & 1.83 & 1.07*** & 1.27 & 0.62*** & 0.73 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.12*** & 1.6 & 0.08*** & 1.16 & 0.06*** & 0.85 & 0.03*** & 0.5 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 6.09*** & 12.85 & 4.25*** & 12.1 & 2.83*** & 10.04 & 1.56*** & 7.82 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.07*** & -4.87 & -0.03*** & -3.81 & -0.02*** & -2.76 & -0.01*** & -1.71 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0*** & -0.72 & 0*** & -0.42 & 0*** & -0.29 & 0*** & -0.25 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.02*** & 0.86 & 0.01*** & 0.47 & 0*** & 0.25 & 0 & 0.05 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences8d_2.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_1 & FA.ses\_1 & FA.d\_2 & FA.ses\_2 & FA.d\_3 & FA.ses\_3 & FA.d\_4 & FA.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 514.85*** & 1.18 & 555.45*** & 0.78 & 600.74*** & 0.78 & 443.13*** & 0.49 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 877212.48*** & 0.53 & 1040106.12*** & 0.36 & 1253555.6*** & 0.35 & 961196.13*** & 0.22 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 5448.5*** & 0.89 & 18489.32*** & 0.91 & 35772.76*** & 1.48 & 39487.59*** & 1.06 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 63.57*** & 1.5 & 83.62*** & 1.59 & 97.82*** & 4.02 & 75.03*** & 2.69 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & -0.02*** & -0.54 & -0.01*** & -0.4 & -0.01*** & -0.22 & 0*** & -0.11 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.13*** & 0.17 & 0.14*** & 0.17 & 0.14*** & 0.18 & 0.13*** & 0.16 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.02*** & 0.39 & 0.01*** & 0.24 & 0.01*** & 0.22 & 0.01*** & 0.16 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.49*** & 0.97 & 0.44*** & 1.4 & 0.43*** & 1.91 & 0.38*** & 2.35 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.02*** & 3.95 & 0.02*** & 2.45 & 0.01*** & 1.65 & 0.01*** & 0.72 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & 0* & -0.25 & -0.01*** & -0.72 & 0*** & -0.77 & 0*** & -0.69 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0*** & -1.09 & 0*** & -1.26 & 0*** & -1.19 & 0*** & -0.67 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.25*** & 7.86 & 0.13*** & 4.81 & 0.05*** & 2.64 & 0.01*** & 0.64 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:18 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_rm1 & FA.ses\_rm1 & FA.d\_rm2 & FA.ses\_rm2 & FA.d\_rm3 & FA.ses\_rm3 & FA.d\_rm4 & FA.ses\_rm4 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 877212.48*** & 0.53 & 1040106.12*** & 0.36 & 1253555.6*** & 0.35 & 961196.13*** & 0.22 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 5448.5*** & 0.89 & 18489.32*** & 0.91 & 35772.76*** & 1.48 & 39487.59*** & 1.06 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 63.57*** & 1.5 & 83.62*** & 1.59 & 97.82*** & 4.02 & 75.03*** & 2.69 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.13*** & 0.17 & 0.14*** & 0.17 & 0.14*** & 0.18 & 0.13*** & 0.16 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.02*** & 0.39 & 0.01*** & 0.24 & 0.01*** & 0.22 & 0.01*** & 0.16 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.49*** & 0.97 & 0.44*** & 1.4 & 0.43*** & 1.91 & 0.38*** & 2.35 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & 0* & -0.25 & -0.01*** & -0.72 & 0*** & -0.77 & 0*** & -0.69 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0*** & -1.09 & 0*** & -1.26 & 0*** & -1.19 & 0*** & -0.67 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.25*** & 7.86 & 0.13*** & 4.81 & 0.05*** & 2.64 & 0.01*** & 0.64 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FA = FA; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences8d_3.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_1 & FI.ses\_1 & FI.d\_2 & FI.ses\_2 & FI.d\_3 & FI.ses\_3 & FI.d\_4 & FI.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 512.45*** & 0.98 & 601.87*** & 0.74 & 538.56*** & 0.54 & 373.2*** & 0.32 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 759454.01*** & 0.51 & 1036742.44*** & 0.41 & 984207.67*** & 0.3 & 724993.83*** & 0.18 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 6282.8*** & 1.77 & 22928.75*** & 1.72 & 33761.59*** & 1.38 & 35235.64*** & 0.95 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 54.91*** & 3.53 & 71.72*** & 3.02 & 67.56*** & 2.39 & 46.86*** & 1.62 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.02*** & 0.45 & 0.01* & 0.15 & 0.01* & 0.15 & 0** & 0.12 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.66*** & 0.77 & 0.45*** & 0.56 & 0.33*** & 0.43 & 0.22*** & 0.29 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.06*** & 0.8 & 0.03*** & 0.5 & 0.02*** & 0.32 & 0.01*** & 0.19 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 1.73*** & 1.99 & 1.19*** & 1.89 & 0.86*** & 2.12 & 0.57*** & 2.4 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.02*** & 1.8 & 0.01*** & 1.45 & 0.01*** & 1.29 & 0*** & 0.52 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.01*** & -0.79 & 0*** & -0.57 & 0*** & -0.49 & 0*** & -0.32 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0*** & -0.96 & 0*** & -0.95 & 0*** & -0.73 & 0*** & -0.5 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.13*** & 1.73 & 0.07*** & 1.59 & 0.03*** & 1.41 & 0.01*** & 0.52 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:56:25 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_rm1 & FI.ses\_rm1 & FI.d\_rm2 & FI.ses\_rm2 & FI.d\_rm3 & FI.ses\_rm3 & FI.d\_rm4 & FI.ses\_rm4 \\ 
  \hline
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 759454.01*** & 0.51 & 1036742.44*** & 0.41 & 984207.67*** & 0.3 & 724993.83*** & 0.18 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 6282.8*** & 1.77 & 22928.75*** & 1.72 & 33761.59*** & 1.38 & 35235.64*** & 0.95 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 54.91*** & 3.53 & 71.72*** & 3.02 & 67.56*** & 2.39 & 46.86*** & 1.62 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.66*** & 0.77 & 0.45*** & 0.56 & 0.33*** & 0.43 & 0.22*** & 0.29 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.06*** & 0.8 & 0.03*** & 0.5 & 0.02*** & 0.32 & 0.01*** & 0.19 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 1.73*** & 1.99 & 1.19*** & 1.89 & 0.86*** & 2.12 & 0.57*** & 2.4 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.01*** & -0.79 & 0*** & -0.57 & 0*** & -0.49 & 0*** & -0.32 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0*** & -0.96 & 0*** & -0.95 & 0*** & -0.73 & 0*** & -0.5 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.13*** & 1.73 & 0.07*** & 1.59 & 0.03*** & 1.41 & 0.01*** & 0.52 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FI = FI; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}
